On the Evolution of Choice Principles

### 2014-07-29 text/RoaM_proceedings/paper.tex
seccom

\begin{abstract}
  We compare the evolutionary competition between different choice
  principles in arbitrary strategic games under one-shot
  interactions. Choice principles under scrutiny are level-$k$
  utility maximization and level-$k$ regret minimization. RESULTS \dots
\end{abstract}

>>>>

\begin{abstract}
  We compare level-$k$ utility maximization and level-$k$ regret
  minimization in evolutionary competition on one-shot plays of
  arbitrary strategic games. RESULTS \dots
\end{abstract}
